\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-25 sections/coverpage.tex
Update coverpage to simpler style

%--------------------------------------------------------%
%	COVER PAGE
%--------------------------------------------------------%

@@

  %\textsc{\LARGE University Name}\\[1.5cm] % Name of your university/college
  \textsc{\Large Manuscript Submission}\\[0.5cm] % Major heading such as course name
  \textsc{\large The Journal of Blah Blah}\\[0.5cm] % Minor heading such as course title

@@

  \vspace{1.5 cm}
  \HRule \\[0.4cm]
  { \huge \bfseries Wordy Manuscript Title: Even Wordier Manuscript Subtitle}\\[0.4cm] % Title of your document
  \HRule \\[1.5cm]

@@

  {\em\Large\textbf Authors:}\\
  \vspace{.5 cm}
  First \textsc{Author}\\
  Department of XYZ,\\
  The University of ABC\\
  \vspace{.5 cm}
  Second \textsc{Author}\\
  Department of XYZ,\\
  The University of ABC\\
  \vspace{.5 cm}
  Third \textsc{Author}\\
  Department of ABC,\\
  XYZ University\\

@@

  \vspace{1.5 cm}
  {\large Submitted: \today}\\[3cm] % Date, change the \today to a set date if you want to be precise

>>>>

%!TEX root = ../main.tex

@@

  %\textsc{\LARGE University Name}\\[1.5cm] % Name of your university/college
  % \textsc{\Large Manuscript Submission}\\[0.5cm] % Major heading such as course name
  % \textsc{\large The Journal of Blah Blah}\\[0.5cm] % Minor heading such as course title

@@

  \vspace{3.5 cm}
  { \huge \bfseries Correlating Microbial Abundances for the Microbial Interaction Network Database}\\[0.4cm] % Title of your document

@@

  \vspace{1.5 cm}
  Dileep Kishore, Gabriel Birzu, Zhenjun Hu, Charles DeLisi, Kirill Korolev, Daniel Segre\\
  \vspace{1cm}
  Department of XYZ,\\
  The University of ABC\\
  Department of ABC,\\
  XYZ University\\

@@

  % \vspace{1.5 cm}
  % {\large Submitted: \today}\\[3cm] % Date, change the \today to a set date if you want to be precise
